---
title: "Invalid Data -Project 1 - Luth -Version 2"
author: "Neelima"
date: "`r strftime(Sys.time(),format='%F %T %Z')`"
output: 
  html_document: 
    toc: true
    theme: united
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r}
ct <- length(unique(luth_data$record_id))

```
**There are `r ct` records in luth - Project 1 Clinical REDCAP database**

***

##**LUTH Project 1**
###**Missing/Discrepancies across all forms for the records in both arms**
**The fields that belong to "enrollment_arm_1 :: HIV_diagnosis" are not missing values but invalid values for the respective records. Please refer to notes in the appendix at the bottom of this page on how to interpret the invalid values in HIV Diagnosis form**


```{r bmi invalid values}
visit_bmi %>%
datatable( rownames = FALSE,class = 'cell-border stripe',
   extensions = c('Buttons','FixedHeader','FixedColumns'),
  options = list(columnDefs = list(list(className = 'dt-right')),
    pageLength = 300, PageWidth =2000, fixedHeader = TRUE, dom = 'Bfrtip', buttons = c( 'colvis', 'print', 'pdf','copy','excel'), scrollY = TRUE, scrollX =TRUE,  fixedColumns = list(leftColumns = 1, rightColumns = 1)
   ) )
```


